### 2011-07-13 poster_gecco/abstract.tex
Added abstract

Creating gaits for legged robots is an important task to enable robots
to access rugged terrain, yet designing such gaits by hand is a
challenging and time-consuming process. In this paper we investigate
various algorithms for automating the creation of quadruped
gaits. Because many robots do not have accurate simulators, we test
gait learning algorithms entirely on a physical robot.  We compare the
performance of two classes of learning gaits: locally searching
parameterized motion models and evolving artificial neural networks
with the HyperNEAT generative encoding.  All parameter search methods
outperform a manually-designed reference gait, but HyperNEAT performs
better still, producing gaits nearly 9 times faster than the reference
gait.

>>>>

Creating gaits for legged robots is an important task to enable robots
to access rugged terrain, yet designing such gaits by hand is a
time-consuming process. We investigate
various algorithms for automating the creation of quadruped
gaits. Because many robots do not have accurate simulators, we test
gait learning algorithms entirely on a physical robot, comparing the
performance of two classes of learning gaits: locally searching
parameterized motion models and evolving artificial neural networks
with the HyperNEAT generative encoding.  All parameter search methods
outperform a manually-designed reference gait, but HyperNEAT performs
better still, producing gaits nearly 9 times faster than the reference
gait.
